---
title: "Issue with readr::read_lines()' skip & n_max"
author: Dan S. Reznik
date: 2019-04-08
output: github_document
---

```{r}
suppressMessages(library(tidyverse))
```

Confirm UTF-8 encoding of included zip file (it contains a larger .txt)

```{r}
fname <- "test_file.zip"
guess_encoding(fname)
```

Read all lines in zip (approx. 31.6k)

```{r}
all_lines <- read_lines(fname)
length(all_lines)
```

```{r,cache=T}
source("./weird_row.R")
weird_row <- find_weird_row(15000,1,length(all_lines))
```

```{r}
cmp_lines <- function(fname,row) {
  ok<-read_lines(fname,
           skip=row,n_max=1)==all_lines[row+1]
  print(sprintf("testing line %d: %s",row,if(ok)"same"else"diff"))
}
cmp_lines(fname,weird_row)
cmp_lines(fname,weird_row+1)
```

The first line to differ appear much later in the file

```{r}
weird_row+1
(read_lines(fname,skip=weird_row+1,n_max=1)==all_lines)%>%which
```

```{r,eval=F,include=F}
all_lines[7380]%>%str_count(";")
all_lines[7380]%>%str_replace_all(fixed(";"),"\n")%>%write_file("7380.txt")
```

Notice all lines have "well-formed" terminations with a carriage-return followed by a newline.

```{r}
{
  s <- read_file(fname)
  print(s %>% str_count("\\r"))
  print(s %>% str_count("\\n"))
  print(s %>% str_count("\\r\\n"))
  print(s %>% str_count("\\n\\r"))
}
```

For this file, the separator is ";" (irrelevant for read_lines()), and there should be 45 per line. However, notice a few lines have a non-standard number of separators (';'), namely: 46 and 48.

```{r}
all_lines %>%
  str_count(";") %>%
  table
```

List which lines have the wrong number of separators, as this will drive us to the bug.

```{r}
all_lines %>%
  str_count(";") %>%
  {which(.!=45)}
```

Use `read_lines()` to read only the first lines with the wrong number of separators, shown above to be line # 14579. So "skip" that number of lines minus one.

```{r}
line1 <- read_lines(fname,
                    skip=14578,
                    n_max=1)
```

Notice its content not only has a different number of separators, it's a different line altogether! (herein lies the bug)

```{r}
all_lines[14579] %>% str_count(";")
line1 %>% str_count(";")
all_lines[14579] == line1
```

Notice the line retrieved by `read_lines(skip=14578,n_max=1)` above actually appears much later in the file, suggesting the reading under this skip+n_max mode lost "sync".

```{r}
(all_lines==line1)%>%which
```

Notes:

  * this bug is not caused by the .zip (same behavior if starts from an uncompressed file)
  * this is not related to encoding, in fact, I made sure the file inside the zip is UTF-8
  * this issue seems to manifest itself with longer files only. potentially there's a character within this file being interpreted as a carriage return.
